Robust Energy-Aware Routing with Uncertain Traffic Demands

### 2015-01-18 paper.tex
begin modify introduction

@@

\author{\IEEEauthorblockN{Heng Lin}
\IEEEauthorblockA{Tsinghua University}
\and
\IEEEauthorblockN{Mingwei Xu}
\IEEEauthorblockA{Tsinghua University}
\and
\IEEEauthorblockN{Yuan Yang}
\IEEEauthorblockA{Tsinghua University}}

@@

\vspace*{0.2in}
\includegraphics[width=8cm]{3-nodes-example}
\vspace*{0.2in}

@@

\vspace*{0.2in}
\includegraphics[width=4cm]{circle}
\includegraphics[width=4cm]{clique}
\vspace*{0.2in}

@@

\vspace*{0.2in}
\includegraphics[width=4cm]{opr_with_remove_links}
\includegraphics[width=4cm]{opr_with_power_saving}
\vspace*{0.2in}

@@

\vspace*{0.2in}
\includegraphics[width=8cm]{power_model}
\vspace*{0.2in}

@@

\vspace*{0.2in}
\includegraphics[width=4cm]{exp2_nosort_abilene}
\includegraphics[width=4cm]{exp2_nosort_geant}
\vspace*{0.2in}

\vspace*{0.2in}
\includegraphics[width=4cm]{exp2_sort_abilene}
\includegraphics[width=4cm]{exp2_sort_geant}
\vspace*{0.2in}

@@

\vspace*{0.2in}
\includegraphics[width=8cm,height=4cm]{exp3_w}
\vspace*{0.2in}

>>>>

\ifCLASSOPTIONcompsoc
    \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\else
    \usepackage[caption=false,font=footnotesize]{subfig}
\fi

@@

\author{\IEEEauthorblockN{Heng Lin}
\IEEEauthorblockA{Tsinghua University \\ henglin1991@gmail.com}
\and
\IEEEauthorblockN{Mingwei Xu}
\IEEEauthorblockA{Tsinghua University \\ xmw@cernet.edu.cn}
\and
\IEEEauthorblockN{Yuan Yang}
\IEEEauthorblockA{Tsinghua University \\ yyang@csnet1.cs.tsinghua.edu.cn}}

@@

\begin{figure}[!t]
\centering
\vspace*{0.1in}
\includegraphics[width=8cm]{3-nodes-example}
\caption{Model Example}
\label{label}
\vspace*{0.1in}
\end{figure}

@@

\begin{figure}[!t]
\centering
\vspace*{0.1in}
\subfloat[Circle]{\includegraphics[width=4cm]{circle}
\label{subfiga}}
\hfill
\subfloat[Clique]{\includegraphics[width=4cm]{clique}
\label{subfigb}}
\caption{Circle and Clique topology of 6 nodes}
\vspace*{0.1in}
\end{figure}

@@

\begin{figure}[!t]
\centering
\vspace*{0.1in}
\subfloat{\includegraphics[width=4cm]{opr_with_remove_links}}
\subfloat{\includegraphics[width=4cm]{opr_with_power_saving}}
\caption{OPR with Power Saving}
\vspace*{0.1in}
\end{figure}

@@

\begin{table}[!t]
\renewcommand{\arraystretch}{1}
\caption{Green TE Power Model}
\label{power model}
\centering
\begin{tabular}{|c|c|c|}
\hline
\bfseries Line-Card & \bfseries Speed(Mbps) & \bfseries Power(Watts) \\
\hline
1-Port OC3 & 155.52 & 60 \\
\hline
8-Port OC3 & 1244.16 & 100 \\
\hline
1-Port OC48 & 2488.32 & 140 \\
\hline
1-Port OC192 & 9953.28 & 174 \\
\hline
\end{tabular}
\end{table}

@@

\begin{figure}[!t]
\centering
\vspace*{0.1in}
\subfloat{\includegraphics[width=4cm]{exp2_nosort_abilene}}
\subfloat{\includegraphics[width=4cm]{exp2_nosort_geant}}
\caption{Nosort: (a). Abilene (b).Geant}
\vspace*{0.1in}
\end{figure}

\begin{figure}[!t]
\centering
\vspace*{0.1in}
\subfloat{\includegraphics[width=4cm]{exp2_sort_abilene}}
\subfloat{\includegraphics[width=4cm]{exp2_sort_geant}}
\caption{Sort: (a). Abilene (b).Geant}
\vspace*{0.1in}
\end{figure}

@@

\begin{figure}
\centering
\vspace*{0.1in}
\includegraphics[width=8cm,height=4cm]{exp3_w}
\caption{OPR with w relationship}
\vspace*{0.1in}
\end{figure}

\section{Related Work}
related work
